\thetitle

### 2020-07-24 writing/challenges.tex
threat from rationality; point to bad type annotations as future work
changing motivation for mutation

One derivative challenge of the first one is the problem of simulating the
programmer's mistakes or, more precisely, the origin of impedance
mismatches. Before a programmer can try to find mistakes, mistakes have to
be made. Technically the problem is the lack of a sufficiently large
available corpus of type errors for a meaningful experiment.
Following~\citet{lksfd-popl-2020} again, the solution is to use mutation
analysis~\cite{lipton1971fault, demillo1978hints, jia2011analysis} to
create mistakes in a synthetic manner. This process yields a large number
of buggy programs whose mixed-typed versions are suitable subjects for our
experiment.  The mutation analysis of Lazarek et al, is, however,
completely useless for creating impedance mismatches.

@@

%Another derivative challenge is the problem of mistakes in type
%annotations themselves.  Gradual typing enables programmers to move an untyped
%code base into the typed realm on an incremental basis. The retroactive addition
%of a specific type to a component, even a library, may result from a
%misunderstanding of the code and may thus be a mistake itself. Anecdotal 
%evidence suggests that this scenario is quite common~\cite{sta-nt-base-types,
%incorrect-ts, wmwz-ecoop-2017}, and hence must be addressed by any evaluation
%method. Conversely, the method not only demands mutators for code that cause
%good impedance mismatches, it also calls for a set of mutators that ``break''
%type annotations without breaking the code itself.

@@

\item Construct a large number of suitable benchmarks for all gradual type
  systems with representative
  type errors  (section~\ref{sec:mutate});

\item Simulate the rational programmer with sufficient 
  modes to (i) match the peculiarities of each gradual type system and 
    (ii) isolate blame from other confounding factors
    (section~\ref{sec:rational});

>>>>

A derivative challenge is the problem of simulating the programmer's
mistakes or, more precisely, the origin of impedance mismatches. Before a
programmer can try to find mistakes, mistakes have to be made.
Specifically, a necessary step to test the rational programmer is to find
a collection of  type mistakes in  mix-typed programs that is highly
representantive of both mistakes and programs ``in the wild.''
Unfortunately no such collection exists.  There is a good reason for that;
the kind of mistakes the rational programmer targets are easily detected
by unit tests and, even if they are tough to weed out, they do not make it
to code repositories.  In other words, the problem is how to generate a
sufficiently large and representantive corpus of type mistakes for a meaningful
experiment.  Following~\citet{lksfd-popl-2020} again, the solution is to
use mutation analysis~\cite{lipton1971fault, demillo1978hints,
jia2011analysis} to create mistakes in a synthetic manner. This process
yields a large number of buggy programs whose mixed-typed versions are
suitable subjects for our experiment.  The mutation analysis of Lazarek et
al, is, however, completely useless for creating impedance mismatches.

@@

@@

\item Generate a large set of programs with representative
  type errors that all three systems can detect (section~\ref{sec:mutate});

\item Simulate the rational programmer on these programs with sufficient 
  modes to (i) match the peculiarities of each  system and 
    (ii) isolate blame from other confounding factors
    (section~\ref{sec:rational});

### 2020-07-24 writing/mutate.tex
changing motivation for mutation

\section{How to Make Benchmarks for Blame} \label{sec:mutate}

An important challenge from~\ref{sec:challenges} is the lack of a large and diverse real-world
 corpus of  mix-typed programs with type errors that we can use to
 evaluate rational programmers. To overcome this issue, 
we create a synthetic corpus of such programs. In this section, we argue
that despite its synthetic nature our corpus of programs is realistic 
and diverse.

>>>>

\section{How to Make Lots of Mistakes} \label{sec:mutate}

An important challenge from~\ref{sec:challenges} is the generation of
mix-typed programs with representative type mistakes. In this section, we
present our generation process and we argue that despite its synthetic
nature it results in a large corpus of programs with type mistakes that
are realistic and diverse.
